Intended Table of Contents Thesis

### 2013-03-08 Chapters/Chapter1/literature_review.tex
Add laboratory / outside settings

Some experiments have only been performed in laboratory settings \cite{yang2008using}, thus probably resulting in less robust trained models.
In \cite{siirtola2012recognizing} the test subjects have performed the testing phase outside, and thus the method is tested in a more natural environment.
\\ *** Elaborate on lab/outside ***.

A more objective comparison can be made based on the segmentation and classification technique used.
In \cite{bao2004activity} and \cite{ravi2005activity} extensive comparisons are made between much used algorithms which are widely implemented, such as in the WEKA toolkit \cite{hall2009weka}.
These include the base-classifiers Decision Trees (also used in \cite{kwapisz2011activity,duque2012offline}), Decision Tables, K-nearest neighbors (also used \cite{duque2012offline, siirtola2012recognizing}), Support Vector Machines (also used in \cite{derawi2010accelerometer,he2009activity, he2008activity}) and Naive Bayes (also used in \cite{long2009single}).
The research of \cite{bao2004activity} also implemented a number of meta-level classifiers, of which Plurality Voting resulted in the highest accuracy.
A very well known and applied algorithm from the field of data mining is $k$-means clustering.
A drawback of this method is that the number of expected clusters needs to be predetermined.
To overcome this shortcoming an interative implementation can be used, which selects the best clustering.
A variant is known as Fuzzy $c$-means clustering, in which a data point can belong to one or more clusters, each with a degree of membership.
The method of $k$-means clustering (or a modified version) is used in \cite{krause2003unsupervised, zhou2008aligned, lee2178physical}.

@@

Inspired on the problems for continuous speech recognition have Hidden Markov Models been applied to activity recognition tasks.
A layered approach proved to be robust for small changes in \cite{perdikis2008recognition}.
In \cite{shi2009towards} five activities have been modeled as HMMs.
The method of \cite{fox2010bayesian} introduces HMMs with Markov Jump Linear Systems to segment a signal, with a fixed number of models.
In \cite{lester2006practical} a layer of HMMs of on top of a layer of static classifiers to estimate the current activity.
This has a commonality with \cite{lester2005hybrid} in which HMMs are used to capture regularities and smooth activity transitions.
The application of \cite{guenterberg2009distributed} constructs separate HHMs for each activity and then joins them in a single model to estimate the likelihood of an activity.

A common property of the above mentioned classification algorithms is that there is no explicit segmentation phase.
Data points can be segmented a posteriori, by joining adjacent data points which have the same label.
An approach in which the data points are processed per segment include \cite{minnen2006discovering}, in which known motifs in the sensor signals are discovered.
In \cite{guenterberg2009automatic} the signal is segmented (without classification) by applying adaptive threshold values on the energy of the signal.
The estimates of the direct density-ratio for probability distributions are compared to create change-points in \cite{kawahara2009change}.
By making minimal model assumptions a non-parametric segmentation is obtained, without classification.
A further application of probability distributions is discussed in \cite{ahmed2012non}, which uses an non-parametric Bayesian method to create an Infinite Gaussian Mixture Model to represent activities.
Very interesting is the ability to recognize past and new activities without training.
The method of \cite{barbivc2004segmenting} considers the intrinsic dimensionality of poses by using Probabilistic Principal Component Analysis and creates cut-points.
This method also is independent of trained models and thus also is a non-parametric approach.
The method of \cite{keogh2001online} creates a piecewise linear representation of the signal as thus approximates it.
This does not result in a segmentation in the sense of some homogeneity over the data points, but it can support one.
In contrast, the method of \cite{himberg2001time} splits and merges segments the signal in a constant number $k$ segments using a cost function to minimize the heterogeity of a segment.

>>>>

Some experiments have only been performed in an artificial or laboratory setting \cite{minnen2006discovering, yang2008using, perdikis2008recognition, guenterberg2009automatic, ravi2005activity, bao2004activity, sherril2005using, he2009activity}, thus probably resulting in less robust trained models.
In \cite{siirtola2012recognizing, kwapisz2011activity} the experiments are performed in a uncontrolled environment.
This results in a more natural setting with more noise due to free movement.
It also introduces transition-states in the data, because there is no clear distinction between activities.
The method of \cite{krause2003unsupervised} explicitly filters the signals for transitions.
Others have provided the test subjects with a measuring device for a longer period of time, some up to a few days \cite{krause2003unsupervised, long2009single}.

A more objective comparison can be made based on the segmentation and classification technique used.
In \cite{bao2004activity} and \cite{ravi2005activity} extensive comparisons are made between much used algorithms which are widely implemented, such as in the WEKA toolkit \cite{hall2009weka}.
These include the base-classifiers Decision Trees (also used in \cite{kwapisz2011activity,duque2012offline}), Decision Tables, K-nearest neighbors (also used \cite{duque2012offline, siirtola2012recognizing}), Support Vector Machines (also used in \cite{derawi2010accelerometer,he2009activity, he2008activity}) and Naive Bayes (also used in \cite{long2009single}).
The research of \cite{bao2004activity} also implemented a number of meta-level classifiers, of which Plurality Voting resulted in the highest accuracy.
A very well known and applied algorithm from the field of data mining is $k$-means clustering.
A drawback of this method is that the number of expected clusters needs to be predetermined.
To overcome this shortcoming an iterative implementation can be used, which selects the best clustering.
A variant is known as Fuzzy $c$-means clustering, in which a data point can belong to one or more clusters, each with a degree of membership.
The method of $k$-means clustering (or a modified version) is used in \cite{krause2003unsupervised, zhou2008aligned, lee2178physical}.

@@

Due similarity with the problem of continuous speech recognition, Hidden Markov Models have been applied to activity recognition tasks.
A layered approach proved to be robust for small changes in \cite{perdikis2008recognition}.
In \cite{shi2009towards} five activities have been modeled as HMMs.
The method of \cite{fox2010bayesian} introduces HMMs with Markov Jump Linear Systems to segment a signal, with a fixed number of models.
In \cite{lester2006practical} a layer of HMMs of on top of a layer of static classifiers to estimate the current activity.
This has a commonality with \cite{lester2005hybrid} in which HMMs are used to capture regularities and smooth activity transitions.
The application of \cite{guenterberg2009distributed} constructs separate HHMs for each activity and then joins them in a single model to estimate the likelihood of an activity.

A common property of the above mentioned classification algorithms is that there is no explicit segmentation phase.
Data points can be segmented a posteriori, by joining adjacent data points which have the same label.
An approach in which the data points are processed per segment include \cite{minnen2006discovering}, in which motifs over sensor data from actions are discovered.
In \cite{guenterberg2009automatic} the signal is segmented (without classification) by applying adaptive threshold values on the energy of the signal.
The estimates of the direct density-ratio for probability distributions are compared to create change-points in \cite{kawahara2009change}.
By making minimal model assumptions a non-parametric segmentation is obtained, without classification.
A further application of probability distributions is discussed in \cite{ahmed2012non}, which uses an non-parametric Bayesian method to create an Infinite Gaussian Mixture Model to represent activities.
Very interesting is the ability to recognize past and new activities without training.
The method of \cite{barbivc2004segmenting} considers the intrinsic dimensionality of poses by using Probabilistic Principal Component Analysis and creates cut-points.
This method also is independent of trained models and thus also is a non-parametric approach.
The method of \cite{keogh2001online} creates a piecewise linear representation of the signal as thus approximates it.
This does not result in a segmentation in the sense of some homogeneity over the data points, but it can support one.
In contrast, the method of \cite{himberg2001time} splits and merges segments the signal in a constant number $k$ segments using a cost function to minimize the heterogeneity of a segment.
